On particular diameter bounds for integral point sets in higher dimensions \footnote{ This work was carried out at Voronezh State University and supported by Russian Science Foundation grant 19-11-00197. }

### 2021-11-06 AvdMomZvol_rails/Article.tex
[AMZr] Edits from Dr. Usachev - page 1

\begin{dfn}
	An integral point set $\mathcal{P}$ is a set of $n$ points in
	the $m$-dimensional Euclidean space $\mathbb{R}^{m}$ with pairwise
	integral distances.
\end{dfn}

How can we characterize an integral point set?
First of all, we can look at its dimension;
then, we can find its cardinality, which is always finite~\cite{anning1945integral,erdos1945integral};
finally, we can naturally % TODO: naturally/essentially? cf. arxiv/1
define the diameter of a finite point set.

@@

@@

@@

For the list of known bounds for $d(m, n)$,
we refer the reader to~\cite[Theorem 1]{kurz2008bounds} or to~\cite{our-vmmsh-2018}.
We will discuss the following ones presented at~\cite{kurz2008bounds}:
\begin{align}
	d(m, 2m + 1) \leq 8\\
	d(m, 2m + 2) \leq 13 \label{eq:d_m_2m+2}\\
	d(m, 3m) \leq 109
\end{align}
and the following theorem \cite[Theorem 2.1]{kurz2008bounds}.

@@

	\begin{equation}\label{formula1}
		d(m, n + 2(m - 2)) \leq \max(w, \operatorname{diam(\mathcal{P})})
	\end{equation}

@@

In this paper we further study the various features of IPS.
In Section 2, we discuss the classification of planar integral points sets;
in Section 3, we present some bounds for $d(m,n)$ based on planar integral point sets of special types
and provide some general constructions of such bounds.

>>>>

\begin{dfn}
	An integral point set $\mathcal{P}$ is a set of $n$ points in
	the $m$-dimensional Euclidean space $\mathbb{R}^{m}$ with pairwise
	integral distances,
	such that $\mathcal{P}$ is not contained in a $(m-1)$-dimensional hyperplane.
\end{dfn}

How can we characterize an integral point set?
First of all, we can look at its dimension;
then, we can find its cardinality, which is always finite~\cite{anning1945integral,erdos1945integral};
finally, we can compute the diameter of a finite point set,
which is naturally defined as follows:

@@

The following notion was introduced in~\cite{kurz2008bounds}.

@@

The computation of exact values of $d(m,n)$ is a difficult problem.
In 2003, Solymosi proved~\cite{solymosi2003note} that $d(2,n) \geq cn$ for some constant $c$;
now it is known~\cite{my-pps-linear-bound-2019} that $c>5/11$.
So, even finding the estimates is not easy.

@@

A long list of known bounds for $d(m, n)$ and some exact values
can be found in~\cite[Theorem 1]{kurz2008bounds} or in~\cite{our-vmmsh-2018}.
Below we will discuss the following ones presented at~\cite{kurz2008bounds}:
\begin{align}
	d(m, 2m + 1) \leq 8\\
	d(m, 2m + 2) \leq 13 \label{eq:d_m_2m+2}\\
	d(m, 3m) \leq 109
\end{align}
and the following theorem \cite[Theorem 2.1]{kurz2008bounds}.

@@

	\begin{equation}\label{formula1}
		d(m, n + 2(m - 2)) \leq \max(w, \operatorname{diam}(\mathcal{P}))
	\end{equation}

@@

In this paper we further study the various features of IPS.
In Section 2, we discuss the classification of planar integral points sets;
in Sections 3 and 4, we present some bounds for $d(m,n)$ based on planar integral point sets of special types
and provide some general constructions of such bounds.
